Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-06-14 paper/ms.tex
going trhough the minor comments on the referee report and the paper

A different approach to infer the typical mass of halos hosting
LAEs is based on the spatial clustering information. 
This approach uses the fact
that in CDM cosmologies the spatial clustering of galaxies on large
scales is entirely dictated by the halo distribution
\citep{Colberg00}, which in turn has a strong dependence on halo
mass. 
Using measurements of the angular correlation function of LAEs,
observers have put constraints on the typical mass and occupation
fraction of the putative halos hosting these galaxies
\citep{Hayashino2004,Gawiser07,Nilsson2007,Ouchi2010,Bielby16}. 
In these studies the observations are done on fields of $\sim 1$ deg$^{2}$ and
the conclusions derived on the halo host mass do not elaborate on the
uncertainty resulting from the cosmic variance on these fields.

In this paper we investigate the impact of cosmic variance in
constraining the mass and occupation fraction of halos hosting LAEs at $z=3$.
We build mock surveys from a cosmological N-body simulation to compare them
against the observations of \cite{Bielby16} using the angular
correlation function.  
We use a simple model to populate a halo in the simulation with a LAE   
assuming a minimum, \mmin, and maximum mass, \mmax, for the dark
matter halos hosting LAEs. We do not  assume  an underlying relation 
between the \ly\  luminosity and the dark matter halo mass.  
This approach bypasses all the physical uncertainties associated to
star formation and radiative transfer. 
We then use the Markov Chain Monte Carlo technique to obtain the
likelihood of the parameters given the observational constraints.

@@

\subsection{Observational constraints}
\label{subsec:obs}
\citet{Bielby16} used narrow band imaging to detect 643 LAE candidates
at $z\sim 3$  with Ly-$\alpha$ rest-frame equivalent widths $\gtrsim$65\AA\ and a  Ly-$\alpha$ flux limit
of $2\times10^{17}{\rm erg/cm^2/s}$ ($L\sim 7\times10^{42}{\rm erg/s} $). 
Using follow-up spectroscopy they found a 22\% contamination fraction $f_{\rm c}$.
Their observations cover 5 (out of 9) independent and adjacent
fields of the VLT LBG Redshift Survey (VLRS).  
The  total observed  area corresponds to 1.07$\rm deg^2$ that translates to
$\sim$80$^2\hMpc^2$ in a comoving scale. 
\citet{Bielby16} used the NB497  narrow-band filter whose 77\AA\ FWHM
and 154\AA\ Full width  tenth maximum (FWTM) correspond to a total observational comoving depth of
44\hMpc\  and 82\hMpc, respectively.

@@

The result in Eq.(\ref{eq:focc}) can be qualitatively understood as
follows.   
A choice of $\focc<1$ means that the halo mass function is scaled down.
If \mmin\ decreases the total number of halos increases because less
massive halos are more abundant.
This requires smaller values of $\focc$ to keep the total
number of halos equal to the number of LAES in observations.

@@

@@

>>>>

A different approach to infer the typical mass of halos hosting
LAEs is based on the spatial clustering information. 
This approach uses the fact
that in CDM cosmologies the spatial clustering of galaxies on large
scales is entirely dictated by the halo distribution
\citep{Colberg00}, which in turn has a strong dependence on halo
mass. 
Using measurements of the angular correlation function of LAEs,
observers have put constraints on the typical mass and occupation
fraction of the putative halos hosting these galaxies
\citep{Hayashino2004,Gawiser07,Nilsson2007,Ouchi2010,Bielby16}. 
In these studies the observations are done on fields of $\sim 1$ deg$^{2}$ and
the conclusions derived on the halo host mass do not elaborate deeply on the
uncertainty resulting from the cosmic variance on these fields. {\bf  \citet{Guaita2010} attempted to analytically 
estimate the uncertainty from cosmic variance 
following \citet{Somerville2004} and \citet{Peebles1980}. Their prescription assumes 
that the correlation function can represented by a power-law $\psi\left(r\right)=\left(r_{0}/r\right)^{\gamma}$. Their estimation of cosmic variance strongly depends on $r_{0}$ and $\gamma$. However, $\gamma$ is only  poorly constrained with current observations which in turns indicates that their cosmic variance estimation could not be precise.}

In this paper we investigate the impact of cosmic variance in
constraining the mass and occupation fraction of halos hosting LAEs at $z=3$.
We build mock surveys from a cosmological N-body simulation to compare them
against the observations of \cite{Bielby16} using the angular
correlation function.  
We use a simple model to populate a halo in the simulation with a LAE   
assuming a minimum, \mmin, and maximum mass, \mmax, for the dark
matter halos hosting LAEs.  We do not  assume  an underlying relation 
between the \ly\  luminosity and the dark matter halo mass.  
This approach bypasses all the physical uncertainties associated to
star formation and radiative transfer. 
We then use the Markov Chain Monte Carlo technique to obtain the
likelihood of the parameters given the observational constraints. {\bf This approach 
allow us to estimate cosmic variance directly from simulations without making any assumption 
on the correlation function behavior.}

@@

\subsection{Observational constraints}
\label{subsec:obs}
\citet{Bielby16} used narrow band imaging to detect 643 LAE candidates
at $z\sim 3$  with Ly-$\alpha$ {\bf rest-frame} equivalent widths $\gtrsim$65\AA\ and a  Ly-$\alpha$ flux limit
of $2\times10^{17}{\rm erg/cm^2/s}$ ($L\sim 7\times10^{42}{\rm erg/s} $). 
Using follow-up spectroscopy they found a 22\% contamination fraction $f_{\rm c}$.
Their observations cover 5 (out of 9) independent and adjacent
fields of the VLT LBG Redshift Survey (VLRS).  
The  total observed  area corresponds to 1.07$\rm deg^2$ that translates to
$\sim$80$^2\hMpc^2$ in a comoving scale. 
\citet{Bielby16} used the NB497  narrow-band filter whose 77\AA\ FWHM
and 154\AA\ Full width  tenth maximum (FWTM) correspond to a total observational comoving depth of
44\hMpc\  and 82\hMpc, respectively.

@@

{\bf The result in Eq.(\ref{eq:focc}) can be qualitatively understood as
follows.   
A choice of $\focc<1$ means that the halo mass function is scaled down.
If \mmin\ decreases the total number of halos increases because less
massive halos are more abundant.
This requires smaller values of $\focc$ to keep the total
number of halos hosting LAEs equal to the number of LAEs in observations.}

@@

\bibitem[{{Guaita} {et~al.}(2010){Guaita}, {Gawiser}, {Padilla},
  {Francke}, {Bond}, {Gronwall}, {Ciardullo}, {Feldmeier}, {Sinawa}, {Blanc},
  \& {Virani}}]{Guaita2010}
{Guaita}, L., {Gawiser}, E., {Padilla}, N., {Francke}, H.,
	{Bond}, N.~A., {Gronwall}, C., {Ciardullo}, R., {Feldmeier}, J.~J., 
	{Sinawa}, S., {Blanc}, G.~A., \& {Virani}, S. 2010, \apj, 714, 255

@@

@ARTICLE{2004ApJ...600L.171S,
   author = {{Somerville}, R.~S. and {Lee}, K. and {Ferguson}, H.~C. and 
	{Gardner}, J.~P. and {Moustakas}, L.~A. and {Giavalisco}, M.
	},
    title = "{Cosmic Variance in the Great Observatories Origins Deep Survey}",
  journal = {\apjl},
   eprint = {astro-ph/0309071},
 keywords = {Galaxies: Statistics, Cosmology: Large-Scale Structure of Universe},
     year = 2004,
    month = jan,
   volume = 600,
    pages = {L171-L174},
      doi = {10.1086/378628},
   adsurl = {http://adsabs.harvard.edu/abs/2004ApJ...600L.171S},
  adsnote = {Provided by the SAO/NASA Astrophysics Data System}
}

\bibitem[{{Somerville} {et~al.}(2004){Somerville}, {Lee}, {Ferguson}, {Gardner},
  {Moustakas}, \& {Giavalisco}}]{Somerville2004}
{Somerville}, R.~S., {Lee}, K., {Ferguson}, H.~C.,
	{Gardner}, J.~P., {Moustakas}, L.~A., \& {Giavalisco}, M. 204, \apj,
  600, 171
